On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-26 response.tex

\documentclass[a4paper,11pt]{exam}
\printanswers

\usepackage{color}

\renewcommand{\solutiontitle}{\noindent\textbf{Response:}\par\noindent}

\begin{document}

\title{Response to the Reviews}
\author{Shiyu Ji}
\maketitle

\begin{questions}
\section{Reviewer 1}
\question Several key issues are not presented clearly, making the paper hard to be followed. For instance, the paper discussed the n-truthful property of the proposed mechanism, during which the authors assumed that the proposed mechanism is strategyproof. So, it is better to give a lemma or a theorem to explicitly prove that the proposed mechanism is strategyproof. Actually, only Lemma 3 in this paper is related to this issue. Nevertheless, this Lemma still has not shown the strategyproof property explicitly. This makes the readers hard to follow this paper, especially for the readers who do not know this area very well. The paper requires the reader to be familiar with the theory of auctions. It is better to spend more time giving some background on auctions. 
\begin{solution}
I have made Lemma 3 more clear. Now it clearly states that for the given $n_i$ profile, the discrete crowdsensing game achieves strategyproof equilibrium. I also gave some texts before Lemma 3: before we introduce our main results, we need Lemma 3, which gives the strategyproof equilibrium for the discrete crowdsensing game. Hope by doing this the readers can better follow the logic flow. 
\end{solution}

\question The model in this paper has some limitations. The authors did not consider some important issues in the platform, which are generally concerned in other papers, such as the number of tasks to be finished and the budget constraint of the platform to finish these tasks. When these issues are taken into consideration, the problem might become more difficult. Despite this, it is better to give an explanation or discussion on this, to make the proposed mechanism practical.

\question In this paper, the authors assume that the range of each user’s cost unit is known to the platform and each user has a maximum payment. The proposed mechanism totally relies on the parameters in the assumption. However, the paper did not mention how to get the parameters in a real crowdsensing system.

\question Some important related literatures are missing.

\section{Reviewer 2}
\question In Section VII, the simulations demonstrate that the authors’ crowdsensing incentive mechanism can achieve group strategyproof and n-truthful equilibrium simultaneously. However, if we do not consider the collusion attack problem, how are about the performance of the proposed crowdsensing incentive mechanism compared to other existing ones? The authors did not discuss it.

\question In Page 1, the authors say “But like other penetration analysis, there is no guarantee of guard against unexamined cases”. However, in Page 9, they conclude that the proposed crowdsensing incentive mechanism can resist any collusion attack. So, if there exists an unexamined collusion attack except those ones in the paper, can the  crowdsensing incentive mechanism be against it?  which is not clear in the paper.

\question In Page 4 Section IV, “e” should be modified to “we”.

\question In Page 2, the caption of Table 1  should be on the top of itself.

\section{Reviewer 3}
\question The limitation of this paper is that it only studies two specific types of crowdsensing systems, where the user's participation level is measured by sensing time and the number of sensing tasks respectively. There are also other crowdsensing systems, for example, users can also submit the set of crowdsensing tasks to perform with their cost.

\question For the first type of crowdsensing model, where the user's participation level is measured by sensing time, only a strategyproof, but not group strategyproof, incentive mechanism is described.

\question Typos: 
In Section I, ``For another group of typical crowdsensing game'', ``When the possibility that colluding nodes can trade profit among them''
In Section II.B, ``a equilibrium''
In Section III, ``We also present an example to present''
In Section IV, ``e leverage...''

\section{Reviewer 4}
\question My major concern is that the paper is more of a kind of reverse engineering. The main architecture is similar to those in references [14][17][20]. The analysis tools are almost directly applied to the crowdsensing platform, without addressing the unique features of crowdsensing platform, which is different from other scenarios. My detailed comments are as follows:

\question First, the authors should justify the motivation for users to collude. Normally, crowdsensing users may not be aware of the identity of other users. Collusion is very hard to be conducted when the cost of coordinating colluders’ actions is high. The author did mention that one person may own multiple devices and collude among those devices. But a user may own 2-3 devices, while the entire user population may be on the scale of thousand.

\question I want to know whether the platform utility will be affected by adopting the proposed collusion-resistant mechanism. Equation (2) gives the platform utility, but afterwards there is no theoretical or numerical analysis on the platform utility. The objective of the platform operator may be more focused on utility maximization rather than eliminating all the collusions.

\question Equation (3) and (4) needs clearer explanation. Notations $s*_S$ and $s*_{\overline{S}}$ should be defined. It should be clearly stated that $s*_S$ is the strategy profile of the users in set $S$, and $\overline{S}$ is the complementary set of $S$.

\question It is strange that the required sensing time, computed by the crowdsensing platform, only depends on the reported cost of users, just for the sake of collusion-resistance. The required sensing time is associated with the sensing task itself. I wonder if the collusion-resistant incentive mechanism can only manipulate the payment $p_i$ rather than the required sensing time $t_i$.

\question The evaluation setting is very confusing. I don’t understanding why “a colluded user i’s cost unit is 1.0, and the perturbation size is 2.0. Then this user i has probability of 25\% to claim $s_i$ = 0,01, and 75\% to claim a strategy larger than 0.01” , where did the figures 25\% and 75\% come from? Can it be 10\% and 90\%? Also, if some users collude, they will choose the optimal reported cost rather than randomly choosing a cost to report, which may hurt their utility.  So I don’t think the results in Fig. 5---10 are valid. Also, the utility comparison of the platform operator under non-collusion-resistant and collusion-resistant mechanisms is wanted.

\question Typos, line 50, page 4, left column, “e leverage”. Line 10, page 5, left column, PDG is not defined.
\end{questions}
\end{document}

### 2015-12-26 techreport.tex
Fix t-truthful def: add more notational explanations.
Typo fixed: summarize.
initially add response

\subsection{Profit Trading}
\label{subsec:pt}
We also investigate the profit trading collusions in the crowdsensing game. Since utility can always be represented in some monetary form, the users involved in profit trading collusion can share their own utilities with other colluded users. For example, by taking another strategy profile, the utility of user $A$ increases by 3 units, and the utility of user $B$ decreases by 1 unit. Then user $A$ can send 2 units to $B$ to let each of them earn 1 unit. Since group strategyproof equilibrium does not consider utility transfer, 
%there may exist profit trading as long as some users can increase their \emph{total} utilities by changing their strategies simultaneously. That is, 
it is not strong enough to eliminate the possibility of profit trading. In order to defend against profit trading, we need to achieve the equilibrium in which for any subset of colluded users, their total utilities are maximized. \emph{$t$-Truthfulness} \cite{goldberg2005collusion} describes the extent of profit-trading collusion resistance of the incentive mechanism.
\begin{definition}
\label{def:tt}
\textbf{($t$-Truthfulness)} Let $U$ be the set of all the players. An incentive mechanism can achieve $t$-truthfulness, if for any nonempty subset $S\subseteq U$ such that $|S|\leq t$, for any strategy profile $s$, we have
\begin{equation}
\sum_{i\in S} u_i(s_S^*,s_{\overline{S}})\geq \sum_{i\in S} u_i(s_S,s_{\overline{S}}).
\end{equation}
Here $s^*=\kappa$, the real cost profile.
\end{definition}
Here $t$ is the upper bound of collusion size that the mechanism can resist. It is obvious that by setting $t=N$, a mechanism that can achieve $N$-Truthfulness can always resist any profit trading collusion. 
%In profit trading collusion, by changing strategy profile, the colluded users must ensure their total utilities can increase, even though some of them will suffer losses in their utilities temporarily. This implies profit trading collusion requires complete trust among the involved users.

@@

We temporarily assume there is no profit trading, which will be discussed later. If there is an upper bound of collusion size, then a PDG can resist any such collusion with a much weakened condition. Note that only the users in a circle of the PDG can successfully collude. Let $C$ be the users in one of the smallest circles in the PDG. If $|C|$ is larger than the upper bound of collusion size, then any subset of colluded users cannot contain any circle. Hence the PDG can resist any such collusion with the upper bound. We summerize the discussions as the following corollary.
\begin{corollary}
For any strategyproof crowdsensing game with user utility equation (\ref{eqn:user_utility_2}), if any possible collusion size is no more than $k$, then the game can resist any such collusion without profit trading if the size of the smallest circle in the PDG is larger than $k$.
\end{corollary}
}

@@

{\color{black}
\subsection{Proofs of Collusion and Profit Trading Resistance}
We now show that Algorithm \ref{alg:np} can not only resist collusion attacks (by achieving group strategyproofness), but also eradicate the possibility of any profit trading (by achieving $N$-truthfulness). Parametric Dependency Graph (PDG) will be used to judge whether the strategyproof equilibrium can be group strategyproof or $N$-truthful.

{\color{blue} Before we introduce our main results, we need Lemma \ref{lem:quadratic}, which gives the strategyproof equilibrium for the discrete crowdsensing game. }
\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
%\begin{picture}(4,4)(-1.5,-0.5)
%\put (-4,1){\vector(1,0){4.2}}% draw x axe
%\put (-3,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
%\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
%\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
%\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (-1.4,0.6){$\hat{x}$}
%\put (-1.0,1){\circle{0.1}}
%\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
%\put (-2,-0.5){(a)}% lengend
%
%\put (1,1){\vector(1,0){4.2}}% draw x axe
%\put (2,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(3.2,1.6)(2.25,1.6)(2.0,-0.2)% draw graph
%\qbezier(3.2,1.6)(4.15,1.6)(4.4,-0.2)
%\put(3.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(3,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dash lines
%\multiput(4,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(5,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (3.3,0.6){$\hat{x}$}
%\put (3.0,1){\circle{0.1}}
%\put (1.8,0.6){$\lceil \hat{x}-\frac{1}{2}\rceil$}
%\put (3,-0.5){(b)}% lengend
%\end{picture}
\begin{tikzpicture}
\coordinate (xmin1) at (-4,1);
\coordinate (xmax1) at (0.3,1);
\coordinate (ymin1) at (-3,0);
\coordinate (ymax1) at (-3,3);

@@

\draw (3,-0.5) node {(b)};% lengend
\end{tikzpicture}
\caption{\color{black}Two cases of the parabola symmetric axis. The dashed vertical lines denote $x=k\in\mathbb{Z}$, and each solid vertical line is the symmetric axis of the parabola. Each circled point is the integer closest to the axis.}
\label{fig:quad_prop}
\end{figure}

@@

Now we can show our main results, Theorem \ref{thm:discrete}.
\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and $N$-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}
}
{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy. }
{\color{blue}Also our mechanism is budget feasible, since the payment sum is upper bounded by the budget B, i.e., $\sum_{p_i} < N \cdot P_m \leq B$.}

>>>>

\subsection{Profit Trading}
\label{subsec:pt}
We also investigate the profit trading collusions in the crowdsensing game. Since utility can always be represented in some monetary form, the users involved in profit trading collusion can share their own utilities with other colluded users. For example, by taking another strategy profile, the utility of user $A$ increases by 3 units, and the utility of user $B$ decreases by 1 unit. Then user $A$ can send 2 units to $B$ to let each of them earn 1 unit. Since group strategyproof equilibrium does not consider utility transfer, 
%there may exist profit trading as long as some users can increase their \emph{total} utilities by changing their strategies simultaneously. That is, 
it is not strong enough to eliminate the possibility of profit trading. In order to defend against profit trading, we need to achieve the equilibrium in which for any subset of colluded users, their total utilities are maximized. \emph{$t$-Truthfulness} \cite{goldberg2005collusion} describes the extent of profit-trading collusion resistance of the incentive mechanism.
\begin{definition}
\label{def:tt}
\textbf{($t$-Truthfulness)} Let $U$ be the set of all the players. An incentive mechanism can achieve $t$-truthfulness, if for any nonempty subset $S\subseteq U$ such that $|S|\leq t$, for any strategy profile $s$, we have
\begin{equation}
\sum_{i\in S} u_i(s_S^*,s_{\overline{S}})\geq \sum_{i\in S} u_i(s_S,s_{\overline{S}}).
\end{equation}
Here $s^*=\kappa$, the real cost profile. {\color{blue}$s_S$ and $s_{\overline{S}}$ are the same as Definition \ref{def:gse}.}
\end{definition}
Here $t$ is the upper bound of collusion size that the mechanism can resist. It is obvious that by setting $t=N$, a mechanism that can achieve $N$-Truthfulness can always resist any profit trading collusion. 
%In profit trading collusion, by changing strategy profile, the colluded users must ensure their total utilities can increase, even though some of them will suffer losses in their utilities temporarily. This implies profit trading collusion requires complete trust among the involved users.

@@

We temporarily assume there is no profit trading, which will be discussed later. If there is an upper bound of collusion size, then a PDG can resist any such collusion with a much weakened condition. Note that only the users in a circle of the PDG can successfully collude. Let $C$ be the users in one of the smallest circles in the PDG. If $|C|$ is larger than the upper bound of collusion size, then any subset of colluded users cannot contain any circle. Hence the PDG can resist any such collusion with the upper bound. We summarize the discussions as the following corollary.
\begin{corollary}
For any strategyproof crowdsensing game with user utility equation (\ref{eqn:user_utility_2}), if any possible collusion size is no more than $k$, then the game can resist any such collusion without profit trading if the size of the smallest circle in the PDG is larger than $k$.
\end{corollary}
}

@@

\subsection{Proofs of Collusion and Profit Trading Resistance}
We now show that Algorithm \ref{alg:np} can not only resist collusion attacks (by achieving group strategyproofness), but also eradicate the possibility of any profit trading (by achieving $N$-truthfulness). Parametric Dependency Graph (PDG) will be used to judge whether the strategyproof equilibrium can be group strategyproof or $N$-truthful.

{\color{blue}Before we introduce our main results, we need Lemma \ref{lem:quadratic}, which gives the strategyproof equilibrium for the discrete crowdsensing game.}

\begin{figure}[!t]
\centering{}
\setlength{\unitlength}{1cm}
%\begin{picture}(4,4)(-1.5,-0.5)
%\put (-4,1){\vector(1,0){4.2}}% draw x axe
%\put (-3,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(-1.2,1.6)(-2.15,1.6)(-2.4,-0.2)% draw graph
%\qbezier(-1.2,1.6)(-0.25,1.6)(0,-0.2)
%\put(-1.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(-2,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dashed lines
%\multiput(-1,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(0,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (-1.4,0.6){$\hat{x}$}
%\put (-1.0,1){\circle{0.1}}
%\put (-0.95,0.6){$\lfloor \hat{x}+\frac{1}{2}\rfloor$}
%\put (-2,-0.5){(a)}% lengend
%
%\put (1,1){\vector(1,0){4.2}}% draw x axe
%\put (2,0){\vector(0,1){3.2}} %draw y axe
%\qbezier(3.2,1.6)(2.25,1.6)(2.0,-0.2)% draw graph
%\qbezier(3.2,1.6)(4.15,1.6)(4.4,-0.2)
%\put(3.2,0){\line(0,1){3.2}} % draw solid lines
%\multiput(3,0)(0,0.2){16}{\line(0,1){0.1}}	% draw dash lines
%\multiput(4,0)(0,0.2){16}{\line(0,1){0.1}}
%\multiput(5,0)(0,0.2){16}{\line(0,1){0.1}}
%\put (3.3,0.6){$\hat{x}$}
%\put (3.0,1){\circle{0.1}}
%\put (1.8,0.6){$\lceil \hat{x}-\frac{1}{2}\rceil$}
%\put (3,-0.5){(b)}% lengend
%\end{picture}
\begin{tikzpicture}
\coordinate (xmin1) at (-4,1);
\coordinate (xmax1) at (0.3,1);
\coordinate (ymin1) at (-3,0);
\coordinate (ymax1) at (-3,3);

@@

\draw (3,-0.5) node {(b)};% lengend
\end{tikzpicture}
\caption{Two cases of the parabola symmetric axis. The dashed vertical lines denote $x=k\in\mathbb{Z}$, and each solid vertical line is the symmetric axis of the parabola. Each circled point is the integer closest to the axis.}
\label{fig:quad_prop}
\end{figure}

@@

Now we can show our main results, Theorem \ref{thm:discrete}.
\begin{theorem}
\label{thm:discrete}
For any discrete crowdsensing game with user utility equation $u_i = p_i - \kappa_in_i$, the incentive mechanism given by Algorithm \ref{alg:np} can achieve group strategyproof and $N$-truthful equilibrium.
\end{theorem}
\begin{IEEEproof}
Clearly the utility of each user $i$ is not parametric dependent on any other user strategy. We may view $n_i$ as restricting the $t_i$ in (\ref{eqn:user_utility_2}) onto integers. %Then the statements in Theorem \ref{thm:main} and Theorem \ref{thm:pt} still hold for the case $u_i = p_i - \kappa_in_i$. 
Theorem \ref{thm:main} guarantees that to complete this proof, it suffices to show that the incentive mechanism given by Algorithm \ref{alg:np} can achieve strategyproof equilibrium. For any user $i$, to maximize its utility $u_i = p_i - \kappa_in_i$, $n_i$ must be $\max_{i\in U}\{m-\lfloor \kappa_i/d \rfloor, 0\}$ by Lemma \ref{lem:quadratic}. In other words, there will be no gain if user $i$ makes its strategy $s_i$ different from the true cost unit $\kappa_i$. This fact implies the strategyproof equilibrium.
\end{IEEEproof}

{\color{black}Note that there will be no gain or loss if user $i$ selects any other points within the ($m+1-n_i$)-th interval. Thus a small partition interval is beneficial to the truthful mechanism, since each user has less freedom to perturb the truthful strategy. }
{\color{blue}Also our mechanism is budget feasible, since the payment sum is upper bounded by the budget B, i.e., $\sum_{p_i} < N \cdot P_m \leq B$.}
